Cycle Route Uptake and Scenario Estimation (CRUSE): an approach for developing strategic cycle network planning tools

### 2024-03-26 paper.qmd
review previous comments by Donal were included

Practitioners in Kildare County Council found that the evidence generated *was already valuable* for the development of new cycle routes, especially when making the case during planning applications.
They emphasized that cycle networks are often fragmented, and the tool allows them to demonstrate how individual local schemes can contribute to a larger, interconnected network.
An unexpected piece of feedback from the workshop was the preference for visualizations that directly compare the fast and quiet routes, as they recognize the importance of both types of routes.
In response to this we provided the 'Route types' page for each county, although this functionality is not available in the landing page map due to other feedback requesting a simpler interface.
In comparison with another tool cycling propensity tool, the CRUSE tool was seen by practitioners in Kildare as more user-friendly, with the ability to generate evidence at the route level, which is crucial for planning new cycling infrastructure.
Overall, the workshop participants concluded that the approach filled gap in evidence and will greatly assist in the development of new cycling projects.

@@

Where cycling data is available, the networks align well in terms of network “shape” and the proportion of trips on different parts of the network. There were two suggestions from Declan which have not yet been implemented: the provision of data showing POWSCAR and recreational estimates/data separately, and the need for training on the tool to ensure that all staff can use it effectively. These, and other potential improvements, are discussed in the next section.

>>>>

Practitioners in Kildare County Council found that the evidence generated *was already valuable* for the development of new cycle routes, especially when making the case during planning applications.
They emphasized that cycle networks are often fragmented, and the tool allows them to demonstrate how individual local schemes can contribute to a larger, interconnected network.
An unexpected piece of feedback from the workshop was the preference for visualizations that directly compare the fast and quiet routes, as they recognize the importance of both types of routes.
In response to this we provided the 'Route types' page for each county, although this functionality is not available in the landing page map due to other feedback requesting a simpler interface.
In comparison with another cycling propensity tool, the CRUSE tool was seen by practitioners in Kildare as more user-friendly, with the ability to generate evidence at the route level, which is crucial for planning new cycling infrastructure.
Overall, the workshop participants concluded that the approach filled gap in evidence and will greatly assist in the development of new cycling projects.

@@

There were two suggestions from Declan which have not yet been implemented: the provision of data showing POWSCAR and recreational estimates/data separately, and the need for training on the tool to ensure that all staff can use it effectively. These, and other potential improvements, are discussed in the next section.
